---
title: "Workshop9-collab"
format: html
editor: visual
---

load libraries

```{r}
library(tidyverse) # for wrangling and plotting
library(lterdatasampler) # for data access
library(ggeffects) # for our models
library(here) # for easy file pathing
```




reading in data:
```{r}
data(pie_crab) #reading in plum island ecosystem data set from lterdata package
```


exploratory vis
```{r}
ggplot(aes(x = latitude, y = size), data = pie_crab) + 
  geom_point(color = "skyblue") + 
  labs(x = "Latitude", y = "Size (mm)") + 
  theme_minimal()
```

writing a model 
```{r}
crab_model <- lm(size ~ latitude,
                 data = pie_crab)
par(mfrow = c(2,2))
plot(crab_model)
                 
                 
```

look at diagnostics here

Interpret model
```{r}
summary(crab_model) # look at results)
```
Slope: 0.49 +/- 0.034
Y intercept = -3.6 +/- 1.27

For everyone one unit increase in latitude, we expect to see an increase in crab size of 0.49 +/- 0.034 mm.

model statistics: F(1,390) = 208.5, p < 0.0001, alpha = 0.05, R^2^ = 0.35




general tips:
1. always save and commit and push
do this often!!!
2. talk to collaborators
3. pull changes, otherwise you will get a "merge conflict"
4. pull, work, save, stage, commit, commit message/ tips for collab, push

